### 2024-02-22 documentation/thesis/thesis_document.tex
.

Completed \gls{mri} systems pose significant challenges for
retrospective adjustments, particularly when individual magnets impact
the overall homogeneity of the magnetic field. While deviations in
homogeneity can be measured post-assembly, the intricate task of
readjustment is considered. It is less cost-intensive and less
complicated to measure the magnets proactively, prior to the
finalization of the \gls{mri} system.

@@

Finally, a comprehensive hardware and software framework needs to be
established, which can measure diverse objects using various sensors. In
addition, comments must be made on the suitability of the sensors used
for magnetic field measurements.

@@

The same procedure is used as for the \emph{Linearity} measurement in
chapter \ref{sensor-characterisation-linearity}, except that instead of
moving the linear axis, the temperature of the temperature chamber is
systematically increased from \emph{20\(^{\circ}\)} to
\emph{50\(^{\circ}\)}. Between each of these temperature changes, the
system is given a waiting time of 30 minutes after reaching the target
temperature.

The field of permanent magnets is highly temperature-dependent and can
lose its magnetisation at higher temperatures (typically
\emph{\textgreater=80\(^{\circ}\)} for non-high-quality \emph{Type-N}
magnets \customcite{GKT16}). The temperature range is selected so that it
is within a sufficient range for the application.

>>>>

Completed \gls{mri} systems pose significant challenges for
retrospective adjustments, particularly when individual magnets impact
the overall homogeneity of the magnetic field. While deviations in
homogeneity can be measured post-assembly, the intricate task of
readjustment is considered. It is less cost-intensive and less
complicated to measure the magnets proactively, prior to the
finalization of the \gls{mri} system. \customcite{W14}

@@

A comprehensive hardware and software framework needs to be established,
which can measure diverse objects using various sensors. In addition,
comments must be made on the suitability of the sensors used for
magnetic field measurements.

@@

The field of permanent magnets is highly temperature-dependent and can
lose its magnetisation at higher temperatures (typically
\emph{\textgreater=80\(^{\circ}\)} for non-high-quality \emph{Type-N}
magnets \customcite{GKT16}). The temperature range is selected so that it
lies within a sufficient range for typical subsequent measurement tasks.

The same procedure is used as for the \emph{Linearity} measurement in
chapter \ref{sensor-characterisation-linearity}, except that instead of
moving the linear axis, the temperature of the temperature chamber is
systematically increased from \emph{20\(^{\circ}\)} to
\emph{50\(^{\circ}\)}. Between each of these temperature changes, the
system is given a additional waiting time of \emph{30} minutes after
reaching the target temperature.
